The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-13 draft/ms.tex
Add two figures and captions.

We only describe new additions and revised fields here, but list all
fields in Table~\ref{tab:par}. We divide the fields into categories in consistency with the individual planet page
on exoplanets.org. Some fields are not explicitly included on the page (e.g., the URLs), but are explicitly listed in the downloadable {\tt .csv} file.\footnote{At \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we focus on EOD in this section, the fields apply to all planets on exoplanets.org. For the definition of orbital elements see \cite{Wright2013} . 
%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

@@

%------------------------------------------------------------------------------
ZZZ Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

@@

To display the KOIs in the EDE table, check the ``Kepler" option on the
upper left of the table (default selection only includes ``Orbit
Database", i.e.~the EOD, and ``Other"). They can also be displayed on
plots with the interactive plotting tool of EDE.

@@

ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
planet properties, such as mass-period, mass-radius?

>>>>

We only describe new additions and revised fields here, but list all
fields in Table~\ref{tab:par}. We divide the fields into categories in
consistency with the individual planet page on
exoplanets.org. Figure~\ref{fig:individual} is an example of
individual planet page. Some fields are not explicitly included on the
page (e.g., the URLs), but are explicitly listed in the downloadable
{\tt .csv} file.\footnote{At
  \url{http://exoplanets.org/csv-files/exoplanets.csv}.} Though we
focus on EOD in this section, the fields apply to all planets on
exoplanets.org. For the definition of orbital elements see
\cite{Wright2013} .
%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
\caption{An example page for an individual exoplanet (WASP-14b in this
  case). The numbers listed in each field contain links to the
  reference on ADS. In this example for WASP-14b, we provide the plot
  for the phased RVs, but we are yet to implement such feature for all
  planets with available RV data.}
\label{fig:individual}
\end{figure}

@@

To display the KOIs in the EDE table, check the ``Kepler" option on
the upper left of the table (default selection only includes ``Orbit
Database", i.e.~the EOD, and ``Other"). They can also be displayed on
plots with the interactive plotting tool of EDE (see
Figure~\ref{fig:koi} for an example plot).

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
\caption{An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
  being plotted are the ones in the EOD, including transit planets
  (blue large dots), RV planets (red triangles), and timing planets
  (magenta squares). The KOIs are plotted as black small dots, and
  their masses are calculated using their radii based on mass-radius
  relations from the literature (see Section~\ref{sec:orbit}).}
\label{fig:koi}
\end{figure}
